\title{NOVEL ION TRAPS FOR DETERMINISTIC ION IMPLANTATION AND QUANTUM SIMULATION}

\underline{K. Singer} \index{Singer K}

{\normalsize{\vspace{-4mm}}
Institut f\"{u}r Physik, Staudingerweg 7, 55128 Mainz, Germany

\email kilian.singer@uni-mainz.de}

Microstructured ion traps allow for the deterministic, high resolution implantation of individual laser-cooled ions, and can operate with sympathetically cooled ion species, isotopes or ionic molecules. They therefore offer the basis of an atomic nano-assembler -- a device capable of placing an exactly defined number of atoms or molecules with sub millikelvin energies into solid state substrates with sub-nanometre precision in depth and lateral position [1,2]. Motivated by the general interest in tailored solid-state quantum materials, I present our steps towards deterministic generation of colour centres or quantum dots that can be placed in well-defined geometries to exploit their mutual coupling.

I will also present new planar and three-dimensional trap geometries which allow for the application of variable RF fields for precise positioning of ions in two dimensions. These geometries are of great interest for realizing two-dimensional ion crystals with controllable interactions, and enable novel schemes for the quantum simulation of solid-state spin systems with laser-cooled trapped ions. Also, a novel trap design for the realization of a thermodynamic heat engine with a single ion; simulations and the experimental setup will be shown [3].

{\normalsize
[1] W. Schnitzler, N. M. Linke, R. Fickler, J. Meijer, F. Schmidt-Kaler, K. Singer, Phys. Rev. Lett. \textbf{102}, 070501 (2009).
\vsp

[2] K. Singer, U. G. Poschinger, M. Murphy, P. A. Ivanov, F. Ziesel, T. Calarco, F. Schmidt-Kaler, Rev. Mod. Phys. \textbf{82}, 2609 (2010).
\vsp

[3] O. Abah, J. Ro{\ss}nagel, G. Jacob, S. Deffner, F. Schmidt-Kaler, K. Singer, E. Lutz, arXiv:1205.1362, (2012).
}

\vspace{\baselineskip}
