\title{HIGH-FIDELITY COMPOSITE ROTATION GATES}
% High-Fidelity Composite Rotation Gates

\underline{H. Gevorgyan} \index{Gevorgyan H.} 
%Hayk Gevorgyan

{\normalsize{\vspace{-4mm}
Department of Physics, Sofia University, 5 James Bourchier Blvd, Sofia, Bulgaria



\email haykgev95@gmail.com}

Quantum rotation gates are key elements in various fields of 
high-precision technologies, such as quantum information, nuclear 
magnetic resonance, electron spin resonance, atomic clocks, atomic 
interferometry, retarders and rotators in polarization optics, etc. In 
quantum information processing, rotation gates are the subject of the 
so-called circuit optimization problem. Here we propose to construct 
quantum rotation gates by using composite pulses. Composite pulse 
sequences are an efficient, robust and flexible technique for coherent 
control of quantum systems. They have the remarkable capability to 
efficiently eliminate systematic errors in one, two or even more 
experimental parameters.

There are two main cost parameters of implementation – the overall gate 
error and the overall gate run-time. Our objective is to derive quantum 
rotation gates with the highest possible accuracy, bandwidth and the 
shortest execution time for a certain number of constituent pulses. We 
focus at the high-fidelity Hadamard gate, for which we obtain different 
types of composite pulses, which maintain the fidelity above the 99.99% 
quantum computing benchmark. The first type is constructed by following 
the amplitude structure of the famous BB1 pulse of Wimperis, consisting 
of a nominal $\pi/2$ pulse followed by several nominal pi pulses. The 
second type follows the amplitude structure of the SCROFULOUS sequence 
and consists of a sequence of nominal pi pulses sandwiched by two pulses 
of different pulse area which is a subject of optimization. Thereby we 
obtain two families of high-fidelity composite rotation gates, which 
greatly expand the possible experimental options beyond the BB1 and 
SCROFULOUS pulses.


\vspace{\baselineskip}

