\title{SINGLE-ATOM TRAPPING WITH OPTICAL TWEEZERS FOR DETERMINISTIC CAVITY LOADING}
% Single-atom trapping with optical tweezers for deterministic cavity loading

\underline{M. IJspeert} \index{IJspeert M.} 
%Mark IJspeert

{\normalsize{\vspace{-4mm}
Clarendon Laboratory,
Parks Road,
Oxford,
OX1 3PU,
United Kingdom



\email mark.ijspeert@physics.ox.ac.uk}}

Efficient single-atom single-photon interfaces are essential to many applications in quantum information processing. The potential of such hybrid systems for the delivery of single photons and distributed entanglement has been demonstrated using $^{87}$Rb atoms stochastically loaded into a high-finesse optical cavity to achieve strong coupling [1]. Whilst this source constitutes an excellent testbed, probabilistic loading limits the scalability of its design. In addition, the ballistic transit of atoms across the cavity mode gives rise to time-dependent coupling strengths.

In this work we present techniques for the cooling, trapping and imaging of single atoms [2]. We demonstrate dipole trapping of individual, laser-cooled $^{87}$Rb atoms captured from a magneto-optic trap on time scales exceeding 40s. We analyse the effect of trap depth and optical molasses density on the lifetime and average occupation of the dipole trap. Such a deterministic means of holding a single atom in place is an important step towards the deterministic cavity loading scheme required for a scalable atom-photon quantum interface.

{\normalsize
[1] T. D. Barrett et al., Quantum Science and Technology 4(2), 025008, (2019).
\vsp

[2] N. Holland et al., Journal of Modern Optics 65(18), 2133-2141, (2018).
}

\vspace{\baselineskip}
