\title{ROBUST STIMULATED RAMAN EXACT PASSAGE USING SHAPED PULSES}
% ROBUST STIMULATED RAMAN EXACT PASSAGE USING SHAPED PULSES

\underline{X. Laforgue} \index{Laforgue X.} 
%Xavier Laforgue

{\normalsize{\vspace{-4mm}
Laboratoire Interdisciplinaire Carnot de Bourgogne, Universit\'e Bourgogne Franche-Comt\'e, CNRS UMR 6303, Alain Savary 9, 21078 Dijon, France

Institut f\"ur Angewandte Physik, Technische Universit\"at Darmstadt, Hochschulstra\ss e 6, 64289 Darmstadt, Germany



\email xavier-jacques\_laforgue-marin@etu.u-bourgogne.fr}}

Three-level $\Lambda$-systems are ubiquitous in quantum processes. Many applications are based on our ability of controlling the population transfer in this system. Fine control suitable for quantum information imposes producing robust transfer of population with ultra high fidelity (UH-fidelity), i.e. under the quantum computation infidelity benchmark of $\epsilon<10^{-4}$, between the two ground states of the system, while maintaining a low transient population on the intermediate (often lossy) excited state during the dynamics.

We developed single-shot shaped pulses [1] for UH-fidelity population transfer on a 3-level quantum system in lambda configuration. To ensure high fidelity, we use the Lewis-Riesenfeld (L-R) method to derive a family of solutions leading to an exact transfer, where the solutions follow a single dynamical mode of the L-R invariant. Among this family, we identify a tracking solution with a single parameter to control simultaneously the fidelity of the transfer, the population of the excited state, and robustness. We define a measure of the robustness of an UH-fidelity transfer as the minimum percentile deviation on the pulse areas at which the infidelity rises above $10^{-4}$. The robustness of our shaped pulses is found superior to that of Gaussian and adiabatically-optimized pulses for moderate pulse areas.

{\normalsize
[1] D. Daems, A. Ruschhaupt, D. Sugny, and S. Gu\'erin, Robust quantum control by a single-shot shaped pulse, Phys. Rev. Lett. 111, 050404 (2013).
}

\vspace{\baselineskip}