\title{IMAGING ULTRAFAST STRUCTURAL CHANGES IN ISOLATED CARBONYL SULFIDE MOLECULES USING A ATTOSECOND ELECTRON WAVE PACKET}
% Imaging ultrafast structural changes in isolated carbonyl sulfide molecules using a attosecond electron wave packet

\underline{A. Sanchez} \index{Sanchez A.} 
%Aurelien Sanchez

{\normalsize{\vspace{-4mm}
37 Joaquin Costa 08001 Barcelona



\email aurelien.sanchez@icfo.eu}}

The geometric structure of molecules in excited electronic states has been determined through indirect methods such as pump-probe and rotational spectroscopy measurements. Here, we report the direct structural imaging of carbonyl sulphide (OCS) singly and doubly-charged ion with sub-angstroms spatial and attosecond temporal resolution using laser-induced electron diffraction (LIED) [1]. We employed a similar FT-LIED [2] method as that detailed in our previous work and unambiguously resolve a strongly bent and asymmetrically stretched OCS+ and OCS2+ structures. A comparable mechanism in the presence of a strong mid-infrared field has been previously observed in carbon disulphide (CS$_2$) and explained as a result of symmetry breaking due to the Renner-Teller effect [3]. Additionally, we compared the experimental interference signal in the backscattered direction to theoretical calculations and we find a close agreement with what the independent atomic model (IAM) predicts. Most interestingly, we show that such an enhancement in the theoretical molecular contrast factor (MCF) can be observed only if we consider molecular bonds aligned parallel with the electric field vector. This demonstrates the possibility to use the FT-LIED method as a tool for probing specific molecular bonds with enhanced sensitivity.

{\normalsize
[1] M. G. Pullen et al., Nat. Commun. 6, 7262 (2015).
\vsp

[2] M. G. Pullen et al., Nat. Commun. 7, 11922 (2016)
\vsp

[3] K. Amini et al., Proc. Natl. Acad. Sci. USA., 201817465 (2019).
}

\vspace{\baselineskip}