\title{COMPENSATION OF THE TRAP-INDUCED QUADRUPOLE INTERACTION IN TRAPPED RYDBERG IONS}
% Compensation of the trap-induced quadrupole interaction in trapped Rydberg ions

\underline{L. Simeonov} \index{Simeonov L.} 
%Lachezar Simeonov

{\normalsize{\vspace{-4mm}
Department of Physics, Sofia University, 5 James Bourchier Blvd, Sofia, Bulgaria



\email lsimeonov@phys.uni-sofia.bg}}

The quadrupole interaction between the Rydberg electronic states of a Rydberg ion and the radio
frequency electric field of the ion trap is analyzed. Such a coupling is negligible for the lowest energy
levels of a trapped ion but it is important for a trapped Rydberg ion due to its large electric quadrupole
moment. This coupling cannot be neglected by the standard rotating-wave approximation because it is
comparable to the frequency of the trapping electric field. We investigate the effect of the quadrupole
coupling by performing a suitable effective representation of the Hamiltonian. For a single ion we
show that in this effective picture the quadrupole interaction is replaced by rescaled laser intensities
and additional Stark shifts of the Rydberg levels. Hence this detrimental quadrupole coupling can be
efficiently compensated by an appropriate increase of the Rabi frequencies. Moreover, we consider
the strong dipole-dipole interaction between a pair of Rydberg ions in the presence of the quadrupole
coupling. In the effective representation we observe reducing of the dipole-dipole coupling as well as
additional spin-spin interaction.

\vspace{\baselineskip}
