\title{ULTRAHIGH-FIDELITY COMPOSITE ROTATION GATES}
% Ultrahigh-Fidelity Composite Rotation Gates

\underline{H. Gevorgyan} \index{Gevorgyan H.} 
%Hayk Gevorgyan

{\normalsize{\vspace{-4mm}
Theoretical Physics Division,
Department of Physics, Sofia University,
James Bourchier 5 Blvd, 1164 Sofia, Bulgaria



\email hayk.gevorgyan.international@gmail.com}}

Quantum rotation gates are key elements in various fields of high-precision technologies, such as quantum information, nuclear magnetic resonance, electron spin resonance, atomic clocks, atomic interferometry, retarders and rotators in polarization optics, etc. In quantum information processing (QIP), rotation gates are the subject of the so-called circuit optimization problem. Here we propose to construct quantum rotation gates by using composite pulses, i.e. so-called composite rotation gates (CRGs). Composite pulse sequences are an efficient, robust and flexible technique for coherent control of quantum systems. They have the remarkable capability to efficiently eliminate systematic errors in one, two or even more experimental parameters. There are two main cost parameters of implementation – the overall gate error and the overall gate run-time. Our objective is to derive CRGs with the highest possible accuracy, bandwidth and the shortest execution time for a certain number of constituent pulses. We focus at the high-fidelity Hadamard gate, for which we obtain different types of composite pulses, which maintain the fidelity above the 99.99\% quantum computing benchmark. Separate and simultaneous compensation of different systematic errors is studied numerically. The results significantly expand the possible experimental variants beyond the well-known pulses that are analytically found in the so-called nuclear magnetic resonance quantum computing (NMR QC).

\vspace{\baselineskip}