\title{UNIVERSAL ARBITRARILY ACCURATE PULSE ERROR COMPENSATING SEQUENCES FOR REPHASING AND DYNAMICAL DECOUPLING}
%Universal arbitrarily accurate pulse error compensating sequences for rephasing and dynamical decoupling

\underline{G. Genov} \index{Genov G}

{\normalsize{\vspace{-4mm}
\darmstadt

\email genko.genov@physik.tu-darmstadt.de}}

Dynamical decoupling (DD) is a practical and widely used approach to protect quantum systems from unwanted interactions with the environment by applying sequences of pulses. Most DD schemes and this contribution focus on pure dephasing, which is the main cause for decoherence in various systems, e.g., in nuclear magnetic resonance, optics, and quantum information. Then, the major limitation to DD are pulse imperfections. Most robust DD sequences developed so far compensate pulse errors in one or two parameters only (e.g., flip angle), and some are robust only for a specific initial state. Ultra-high fidelity can potentially by achieved by nesting of sequences, but this requires an exponential growth in the number of pulses.

In this contribution, we describe a general theoretical procedure to derive universal sequences for rephasing and DD, which compensate to an arbitrary order any systematic pulse error for any pulse shape. They also improve the performance for an arbitrary initial condition and require only a linear growth in the number of pulses for higher order error compensation. The only assumptions are for identical phased pulses and a constant effect of the environment on the two-state system during one DD sequence. As a basic example of relevance to many applications in quantum physics, we experimentally demonstrate the concept by DD of atomic coherences for coherent optical data storage in a $\mathrm{Pr}^{3+}:\mathrm{Y}_2\mathrm{SiO}_5$ crystal.

%{\normalsize
%}

\vspace{\baselineskip} 