\title{NON-CLASSICAL CORRELATIONS BETWEEN A C-BAND TELECOM PHOTON AND A STORED SPINWAVE}
%Non-classical correlations between a C-band telecom photon and a stored spinwave

\underline{G. Heinze} \index{Heinze G}

{\normalsize{\vspace{-4mm}
ICFO -- The Institute of Photonic Sciences,
Av. Carl Friedrich Gauss 3,
08860 Castelldefels (Barcelona), Spain

\email georg.heinze@icfo.es}}

Future ground-based quantum information networks will likely use single photons transmitted through optical fibers to entangle individual network nodes. To extend communication distances and overcome limitations due to photon absorption in fibers the concept of quantum repeaters has been proposed. For that purpose, it is required to achieve quantum correlations between the material nodes and photons at telecom wavelengths, which can be sent over long distances in optical fibers.

We report on non-classical correlations between a frequency converted telecom C-band photon and a spin-wave stored in an atomic ensemble quantum memory. The photon, emitted from the ensemble and heralding the spin-wave, is converted from 780 nm to 1552 nm by means of an all-solid-state integrated waveguide non-linear device. We show ultra-low noise operation of the device enabling a high signal to noise ratio of the converted single photon, leading to a high spin-wave heralding efficiency. The presented work is an enabling step towards the practical entanglement of remote quantum memories and the entanglement of quantum systems operating at different wavelengths.

%{\normalsize
%[1] N. Gisin et al., Nat. Photon. \textbf{1}, 165–71 (2007).
%\vsp
%
%[2] H. J. Kimble, Nature \textbf{453}, 1023–30 (2008).
%\vsp
%
%[3] N. Sangouard et al., Rev. Mod. Phys. \textbf{83}, 33 (2011).
%\vsp
%
%[4] W. Tittel et al., Laser Photon. Rev. \textbf{4}, 244 (2010).
%\vsp
%
%[5] L. M. Duan et al., Nature \textbf{414}, 413 (2001).
%\vsp
%
%[6] P. Sekatski et al., Phys. Rev. A \textbf{83}, 053840 (2011).
%\vsp
%
%[7] P. Jobez et al., Phys. Rev. Lett. \textbf{114}, 230502 (2015).
%}



\vspace{\baselineskip} 