\title{STATIONARY LIGHT PULSES IN HOLLOW-CORE FIBER AND DYNAMICAL INVARIANTS FOR PSEUDO-HERMITIAN HAMILTONIANS}
%Stationary light pulses in hollow-core fiber and dynamical invariants for pseudo-hermitian Hamiltonians

\underline{L. Simeonov} \index{Simeonov L}

{\normalsize{\vspace{-4mm}
\unisofia

\email lsimeonov@phys.uni-sofia.bg}}

We present two topics.

The first concerns theoretical investigation and the first observation of stationary light pulses \textit{inside} hollow-core fibres. The experiment was conducted by F. Blatt, T. Peters, and T. Halfmann in Darmstadt. Laser-cooled atoms were first loaded into the fiber core providing strong light-matter coupling. Light pulses were then stored in a collective atomic excitation using a single control laser beam. By applying a second counterpropagating control beam, a light pulse could be brought to a standstill. We compare the theoretical and experimental results.

The second topic concerns theoretical derivation of dynamical invariants for a general $N$-state quantum system described by a pseudo-hermitian Hamiltonian. Explicit expressions are presented for two- and three-state systems, which are exemplified by explicit analytic solutions for constant couplings. In the two-state case, we derive
non-hermitian analogs of the Bloch vector and the Bloch equation, customary for hermitian quantum
systems. We suggest possible physical implementations of the dynamical invariants in waveguide
optics and frequency conversion.


\vspace{\baselineskip} 