\title{GENERATION OF COHERENT SUPERPOSITION STATES: EXACT ANALYTICAL MODELS}
%Generation of coherent superposition states: exact analytical models

\underline{K. Zlatanov} \index{Zlatanov K}

{\normalsize{\vspace{-4mm}
\darmstadt
\vspace{-4mm}

\unisofia

\email kaloyan.zlatanov@physik.tu-darmstadt.de}}

States of coherent superposition play a significant role in quantum optics and related fields. Applications are known in high precision measurements, atomic clocks, quantum information, etc. Simple techniques for generating equal superposition states like a resonant $\pi/2$ pulse  do not always work since they are not robust. Among the various more sophisticated techniques are DEQSIE [1], shortcuts to adiabacity and composite pulses for generating such states.

In this contribution we analyze several analytic models for generation of coherent superpositions. Exact analytic solutions can provide simple asymptotic dependence of the excitation probability on the controlling parameters. They can also be used as a base for generation of composite pulses or inverse engineering for single shot shaped pulses.

Often $N$-level systems can be brought via Morris-Shore transformation to a set of two level systems. For that reason the prime concern of our investigation is with two-level systems. The investigation is carried for popular pulse shapes and detuning combinations. We consider excitation in the adiabatic regime and also models that go beyond the adiabatic limit. We show how arbitrary superposition can be generated in the adiabatic limit of the Demkov-Kunike model. We provide asymptotic expansions which generate equal superposition for various models.

{\normalsize
[1] N. V. Vitanov and B. W. Shore, J. Phys. B: At. Mol. Opt. Phys. \textbf{48}, 174008 (2015).
}

\vspace{\baselineskip} 