\title{CRITICAL BEHAVIOR OF ONE DIMENSIONAL ION \mbox{CRYSTALS}}

\underline{G. de Chiara} \index{de Chiara G}

{\normalsize{\vspace{-4mm}
Grup d'Optica, Universitat Autonoma de Barcelona, Spain

\email gabriele.dechiara@uab.es}}

A one dimensional ion chain, confined by a harmonic potential, exhibits a sudden transition to a zigzag configuration when the
radial potential reaches a critical value. Here we show that this structural change is a phase transition of second order, whose
order parameter is the crystal displacement from the chain axis. We study analytically the transition using Landau theory and
find full agreement with numerical predictions. Our theory [1] allows us to determine analytically the system's behaviour at the
transition point. In addition, we show that the statistical properties of a Coulomb crystal can be measured by means of a Ramsey
interferometry procedure performed on the spin of one ion in the chain [2]. The ion spin, constituted by two internal levels of
the ion, couples to the crystal modes via spatial displacement induced by photon absorption. The loss of contrast in the
interferometric signal allows one to measure the autocorrelation function of the crystal observables. Close to the linear-zigzag
transition point, the signal reveals information on the critical properties of the crystal.

\vspace{-4mm}
{\normalsize
\begin{enumerate}
\item S. Fishman, G. De Chiara, T. Calarco, G. Morigi, %: ``Structural phase transitions in low-dimensional ion crystals'',
Phys. Rev. B \textbf{77}, 064111 (2008).
\item S. Fishman, G. De Chiara, T. Calarco, G. Morigi, %: ``Ramsey interferometry with a spin embedded in a Coulomb chain'',
Phys. Rev. A \textbf{78}, 043414 (2008)
\end{enumerate}
}

\vspace{\baselineskip}