\title{OPTICALLY DRIVEN ATOMIC COHERENCES: FROM THE GAS PHASE TO THE SOLID STATE}

\underline{T. Halfmann} \index{Halfmann T}

{\normalsize{\vspace{-4mm}
Institute of Applied Physics, Technical University of Darmstadt,
64289 Darmstadt, Germany

\email thomas.halfmann@physik.tu-darmstadt.de}}

Interactions between strong, coherent radiation (i.e. lasers) and
matter (i.e. quantum systems) provide well-established and powerful
tools to control optical properties and processes in any type of
quantized medium. Among others, contemporary research efforts aim at
efficient storage and processing of optically encoded data, e.g. as
required in quantum information processing. Thus, a large number of
experimental studies in quantum information science have been
conducted in atomic media in the gas phase (i.e. media of very low
storage density). Only few experiments on coherent interactions were
conducted in solid state media.

The talk presents experimental implementations of coherent
laser-driven interactions in particular solid media, i.e. rare-earth
doped solids. The latter media combine the advantages of atoms in
the gas phase (i.e. spectrally narrow transitions) with the
advantages of solids (i.e. large density and scalability). The talk
reports on the experimental implementation of rapid adiabatic
passage (RAP) to switch between absorption and amplification in the
crystal, stimulated Raman adiabatic passage (STIRAP) to manipulate
atomic population distributions, and electromagnetically-induced
transparency (EIT) to store and retrieve light pulses (e.g.
optically encoded information) in a rare-earth doped solid.

\vspace{-4mm} {\normalsize \begin{enumerate}
\item J. Klein, F. Beil, and T. Halfmann, %Robust Population Transfer by Stimulated Raman Adiabatic Passage in a Pr3+:Y2SiO5 Crystal,
Phys. Rev. Lett. \textbf{99}, 113003 (2007).
\item J. Klein, F. Beil, and T. Halfmann, %Experimental Investigations of Stimulated Raman Adiabatic Passage in a Doped Solid,
Phys. Rev. A \textbf{78}, 033416 (2008).
\item F. Beil, J. Klein, G. Nikoghosyan, and T. Halfmann, %Electromagnetically induced transparency and retrieval of light pulses in a $\Lambda$-type and a V-type level scheme in Pr3+:Y2SiO5,
J. Phys. B \textbf{41}, 074001 (2008).
\end{enumerate}
}

\vspace{\baselineskip}