\title{QUANTUM-LIKE PHENOMENA AND NONLINEAR OPTICAL FREQUENCY CONVERSION IN COUPLED WAVEGUIDES}

\underline{G. Montemezzani} \index{Montemezzani G}

{\normalsize{\vspace{-4mm}
Laboratoire Mat\'eriaux Optiques, Photonique et Syst\`emes (LMOPS),
Universit\'e de Lorraine et Sup\'elec 2, rue E. Belin
57070 METZ (France)

\email germano.montemezzani@metz.supelec.fr}}

The equations governing the evanescent coupling of light between dielectric optical waveguides present a formal analogy with the Schr\"{o}dinger equation describing the quantum population dynamics among coupled quantum levels in the rotating wave approximation. These analogies are inspiring increasing interest in fundamental studies as well as for potential applications in integrated optics. We will first summarize our recent studies in this context, for which we employ an experimental platform permitting the photo-inscription of reconfigurable waveguides. The attention will be focused on our recent investigations on waveguide structures with waveguide propagation constant evolving along the longitudinal propagation direction, which permit to verify the analogy to phenomena such as the two-state Stimulated-Raman Adiabatic Passage (two-state STIRAP).
Coupled waveguides hold interest also for applications in nonlinear frequency conversion. Specifically, the back-and-forth bouncing of light between two waveguides allows in principle to realize a wealth of new phase-matching conditions for different types of nonlinear optical interactions. The second part of the talk will illustrate the theoretical framework that we have recently developed for such very rich phenomena, that we have called ``Coupling Length Phase Matching'' (CLPM). Illustrating examples for sum- and difference-frequency generation, second-harmonic generation, as well as third-order type three-wave interactions will be given.

\vspace{\baselineskip}
