\title{COMPOSITE PULSES FOR THREE-STATE QUANTUM SYSTEMS}

\underline{G. T. Genov}, B. T. Torosov, N. V. Vitanov  \index{Genov G}\index{Torosov B}\index{Vitanov N}

{\normalsize{\vspace{-4mm}
\unisofia

\email genko.genov@quantum-bg.org}}

Composite pulses are used in nuclear magnetic resonance [1,2], and most recently, in trapped-ion quantum information processing [3], for design of qubit rotations that are more robust against variations in the pulse area and/or the detuning than single resonant pulses of precise area. The composite pulse is a sequence of pulses with well defined relative phases between each other. The composite pulses can be considered as an alternative method to adiabatic pulses with similar robustness and higher fidelity.

In this work we describe the design of composite pulses for three-state chainwise connected quantum systems. These pulses can be used in three different situations depicted. For equal couplings and equidistant detunings, we use the Majorana decomposition [4,5] to reduce the dynamics to an effective two-state system, which allows us to find the three-state propagator analytically and use the pool of available composite pulses. For different couplings and two-photon resonance, we use the Morris-Shore decomposition [6], which again reduces the dynamics to an effective two-state problem and allows us to find the propagator analytically. Finally, in the general case of different couplings and different detunings, we resort to numerical simulation [7].

\begin{enumerate}
\item M. H. Levitt, Prog. NMR Spectrosc. \textbf{18}, 61 (1986).
\item S. Wimperis, J. Magn. Reson. \textbf{109}, 221 (1994).
\item H. H\"{a}ffner, C.F. Roos, and R. Blatt, Phys. Rep. \textbf{469}, 155 (2008).
\item E. Majorana, Nuovo Cimento \textbf{9}, 43 (1932).
\item F. Bloch and I. I. Rabi, Rev. Mod. Phys. \textbf{17}, 237 (1945).
\item J. R. Morris and B. W. Shore, Phys. Rev. A \textbf{27}, 906 (1983).
\item G. T. Genov, B. T. Torosov, and N. V. Vitanov, to be published.
\end{enumerate}

\vspace{\baselineskip} 