\title{SINGLE PHOTONS MADE-TO-MEASURE}

\underline{G. S. Vasilev}$^{1,2}$, D. Ljunggren$^{2,3}$, A.
Kuhn$^{2}$, \index{Vasilev G}\index{Ljunggren D}\index{Kuhn A}

{\normalsize{

\vspace{-4mm} $^1$\unisofia

\vspace{-4mm} $^2$University of Oxford Clarendon Laboratory Parks
Road, Oxford OX1 3PU United Kingdom

\vspace{-4mm} $^3$Dept. of Applied Physics, KTH - Royal Institute
of Technology, 106 91 Stockholm, Sweden

\email gvasilev@phys.uni-sofia.bg}}

We investigate the efficiency of atom-cavity based
photon-generation schemes to deliver single photons of arbitrary
temporal shape. Our model applies to Raman transitions in
three-level atoms with one branch of the transition driven by a
laser pulse, and the other coupled to a cavity mode. For any
possible shape of the single-photon wavepacket, we derive an
unambiguous analytic expression for the shape of the required
driving laser pulse. We furthermore discuss the constraints
limiting the maximum probability for emitting any desired photon,
and use these to estimate upper bounds for the efficiency of the
process. The model is not only valid for Vacuum-Stimulated Raman
Adiabatic Passages (V-STIRAP) in the strong-coupling and
bad-cavity regime, but it generally allows controlling the
coherence and population flow in any Raman process.

\begin{enumerate}
\item A. Kuhn, M. Hennrich, T. Bondo, and G. Rempe, Appl. Phys. B, \textbf{69}, 373–377 (1999).

\item J. I. Cirac, P. Zoller, H. J. Kimble, and H. Mabuchi, Phys. Rev. Lett., \textbf{78}, 3221–3224, (1997).

\item  G. S. Vasilev, A. Kuhn, and N. V. Vitanov, Phys. Rev. A, \textbf{80}, 013417, (2009).

\item  J. C. Garrison and R. Y. Chiao. Quantum Optics. Oxford University Press, (2008).
\end{enumerate}

\vspace{\baselineskip} 