\title{ROBUST QUANTUM CONTROL BY SHAPED PULSES}

\underline{S. Gu\'erin} \index{Gu\'erin S}

{\normalsize{\vspace{-4mm}
\dijon

\email sguerin@u-bourgogne.fr}}

The control of quantum systems by external fields (such as laser and cavity) is at the heart of modern applications ranging from quantum information processing to the control of chemical reactions.
It can be in general formulated as the control of population transfer between photonic, atomic and molecular levels [1].
One of the most challenging issues is the ability to achieve a high-fidelity transfer to a given target state in a robust way with respect to fluctuations, the partial knowledge of the system, and decoherence.  We present techniques that allow the design of fields for such a robust control, ranging from optimal adiabatic methods [2] to composite single-pulse [3] and multi-pulse [4].

Applications to the shaping of multiphoton states leaking out from a cavity driven by a laser field [5], and to the production of adiabatic qudit gates are presented [6].

{\normalsize
[1] S. Gu\'erin and H.R. Jauslin, Adv. Chem. Phys. \textbf{125}, 147 (2003).
\vsp

[2] S. Gu\'erin, V. Hakobyan, and H.-R. Jauslin, Phys. Rev. A  \textbf{84}, 013423 (2011).
\vsp

[3] D. Daems, A. Ruschhaupt, D. Sugny, and S. Gu\'erin, arXiv:1304.4016 (2013).
\vsp

[4] B. T. Torosov, S. Gu\'erin, N. V. Vitanov, Phys. Rev. Lett. \textbf{106}, 233001 (2011).
\vsp

[5] A. Gogyan, S. Gu\'erin, C. Leroy, and Yu. Malakyan, Phys. Rev. A \textbf{86}, 063801 (2012).
\vsp

[6] B. Rousseaux, S. Gu\'erin, and N. V. Vitanov, Phys. Rev. A \textbf{87}, 032328 (2013).
}

\vspace{\baselineskip}
