\title{PHOTON COINCIDENCE COUNTING IN THE ULTRA-STRONG COUPLING REGIME}

\underline{M. Hartmann} \index{Hartmann M}

{\normalsize{\vspace{-4mm}
Technische Universit\"{a}t M\"{u}nchen, Physik Department, T34 James Franck Strasse, 85748 Garching, Germany

\email michael.hartmann@ph.tum.de}}

We report calculations for photon coincidence counting statistics in the ultra-strong coupling regime, where the strength of the interaction between a quantum emitter and the cavity photons becomes comparable to the transition frequency of the emitter or the resonance frequency of the cavity mode. In such a regime of interaction, the usual normal order correlation functions fail to describe the output photon statistics and the rotating-wave approximation breaks down. By exploiting correct, generalized input-output relations within a suitable master equation approach, we are able to propose correlation functions that are valid for arbitrary degrees of light-matter interaction. In particular, here we focus on the photon blockade effect for a coherently driven system [1] and the emission of non-classical light from thermal systems [2]. We find significant deviations from the standard scenarios showing that the emission characteristics of cavity systems in ultra-strong coupling display quite unexpected physical behavior.

{\normalsize
[1] A. Ridolfo, M. Leib, S. Savasta, and M. J. Hartmann, Phys. Rev. Lett. \textbf{109}, 193602 (2012).
\vsp

[2] A. Ridolfo, S. Savasta, and M. J. Hartmann, Phys. Rev. Lett. \textbf{110}, 163601 (2013).
}

\vspace{\baselineskip}
