\title{COLLISIONS OF ULTRACOLD POLAR MOLECULES IN MICROWAVE TRAPS}

\underline{A. Avdeenkov}$^{12}$

\index{Avdeenkov A}

$^1$ National Institute for Theoretical Physics, Stellenbosch Institute of Advanced Study, Private BagX1, Matieland, 7602, South Africa\\
$^2$ Institute of Nuclear Physics, Moscow State University, Moscow, 119992, Russia\\
email: avdeenkov@sun.ac.za

The collisions between linear polar molecules, trapped in a microwave field with a circular polarization, are theoretically analyzed. The microwave trap suggested by DeMille[1] seems to be rather advantageous in comparison with other traps. Here we have demonstrated that the microwave trap can provide the successful evaporative cooling for polar molecules not only in their absolute ground state but also in almost any strong-field seeking states and the collision losses should not be of much concern to them [2]. But the state in which molecules can be safely loaded and trapped depends on the frequency of the AC-field. The AC-Stark splitting is characterized by $\left|J,M,n\right>$ states, where $M$ is the projection of rotation spin $J$ and n is the deviation of the photon number. We are mostly interested in the lowest energy strong-field-seeking state of the ground vibrational state, $\left|JM\right>= \left|00\right>$ and found rather large inelastic cross sections for molecules even in this state. But we found that the nature of this inelasticity is simply the ``undressing'' of molecules by one photon each and should not cause the loss of molecules from the trap.

[1] D. DeMille, D. R. Glenn, and J. Petricka, Microwave traps for cold polar molecules Euro. Phys.J.D 31, 375 (2004)\newline
[2] A.V.Avdeenkov, Collisions of bosonic ultracold polar molecules in microwave traps, New J. Phys. 11 (2009)(accepted for publication)\newline
[3] A.V.Avdeenkov and J.L.Bohn, Collisional dynamics of ultracold OH molecules in an electrostatic field, Phys.Rev. A, 66, 052718(2002)

\vspace{\baselineskip}