\title{NON MARKOVIAN DYNAMICS OF BIPARTITE ENTANGLEMENT}

\underline{S. Maniscalco}

\index{Maniscalco S}

Department of Physics and Astronomy, University of Turku, 20014 Turku, Finland\\
email: smanis@utu.fi

The non-Markovian dynamics of entanglement between two-qubits and between two continuous variable quantum channels is
investigated.
For the case of two qubits immersed in a common environment, we demonstrate the optimal conditions for reservoir-mediated
entanglement generation and we study the effects of the reservoir memory on entanglement deterioration [1,2].
We then consider two possible strategies for protecting two-qubit entanglement for both the common reservoir and the
independent reservoir cases [3,4].
Finally we tackle the problem of the non-Markovian description of the time evolution of entanglement in continuous variable
quantum channels [5] and we compare the dynamics of entanglement loss for different types of structured reservoirs.

[1] F. Francica, S. Maniscalco, J. Piilo, F. Plastina, and K.-A. Suominen, Phys. Rev. A \textbf{79}, 032310 (2009).\newline
[2] L. Mazzola, S. Maniscalco, J. Piilo, K.-A. Suominen, and B. M. Garraway, Phys. Rev. A \textbf{79}, 042302 (2009).\newline
[3] S. Maniscalco, F. Francica, R. L. Zaffino, N. Lo Gullo, and F. Plastina, Phys. Rev. Lett. \textbf{100}, 090503 (2008).\newline
[4] B. Bellomo, R. Lo Franco, S. Maniscalco, and G. Compagno Phys. Rev. A \textbf{78}, 060302(R)Â (2008).\newline
[5] S. Maniscalco, S. Olivares, and M. G. A. Paris, Phys. Rev. A \textbf{75}, 062119 (2007).

\vspace{\baselineskip}