\title{COHERENT TRANSIENTS IN THE FORMATION OF ULTRACOLD MOLECULES WITH SHAPED FEMTOSECOND PULSES}

\underline{T. G. Mullins}$^1$, W. Salzmann$^1$, S. G\"{o}tz$^{12}$, M. Albert$^1$, J. Eng$^1$, R. Wester$^1$, M. Weidem\"{u}ller$^{12}$\\
A. Merli$^3$, S. Weber$^3$, M. Plewicki$^3$, F. Sauer$^3$, F. Weise$^3$, L. W\"{o}ste$^3$, A. Lindinger$^3$

\index{Mullins T, Salzmann W}
\index{Mullins T}
\index{Mullins T}
\index{Mullins T}
\index{Mullins T}


$^1$Physikalisches Institut,
Universit\"{a}t Freiburg,
Hermann-Herder-Str. 3,
79104 Freiburg,
Germany\\
$^2$Ruprecht Karls Universit\"{a}t Heidelberg, D-69120 Heidelberg, Germany\\
$^3$Fachbereich Physik der Freien Universit\"{a}t Berlin, D-14195 Berlin, Germany\\
email: terry.mullins@physik.uni-freiburg.de

We present experiments on the formation of ultracold molecules by femtosecond laser pulses in a pump-probe scheme [1]. Previous experiments [2,3] have only managed to dissociate molecules by femtosecond pulses, whereas now active photoassociation is observed. A shaped pump pulse excites a collision pair of laser cooled rubidium atoms to a bound molecular state below the $5s5p_{1/2}$ asymptote, from where the molecule is transferred to the molecular ionic state by a probe pulse a few picoseconds later. A femtosecond pulse shaper is used to apply a sharp low-pass optical filter to the pump pulse spectrum with a cut-off frequency a few wavenumbers below the atomic D1 resonance. The photoassociation signal shows oscillatory dynamics between the electronic molecular states coupled by the pump pulse, resulting from the pump pulse's high electric field strength and its specific spectral shape close to the molecular dissociation limit. Simulations of the pump pulse excitation have been performed by numerically solving the time-dependent Schr\"{o}dinger equation using a mapped-fourier-grid-hamiltonian algorithm and are in excellent agreement with the experimental results.

[1] W. Salzmann et al., Phys. Rev. Lett. \textbf{100}, (2008) 233003.\newline
[2] W. Salzmann et al., Phys. Rev. A \textbf{73}, (2006) 023414.\newline
[3] B. L. Brown et al., Phys. Rev. Lett. \textbf{96}, (2006) 173002.\newline
[4] M. J. Wright et al., Phys. Rev. A \textbf{75}, (2007) 051401.

\vspace{\baselineskip}