\title{OPTIMUM PULSE SHAPES FOR STIMULATED RAMAN ADIABATIC PASSAGE}

\underline{G. Vasilev}$^{12}$, A. Kuhn$^2$, and N. V. Vitanov$^{23}$

\index{Vasilev G}
\index{Kuhn A}
\index{Vitanov N}

$^1$Department of Physics, University of Oxford, Parks Road, OX1 3PU Oxford, United Kingdom\\
$^2$Department of Physics, Sofia University, 5 James Bourchier 5 Blvd., 1164 Sofia, Bulgaria\\
$^3$Institute of Solid State Physics, Bulgarian Academy of Sciences, Tsarigradsko chauss\'{e}e 72, 1784 Sofia, Bulgaria

Stimulated Raman adiabatic passage (STIRAP) is a well established
and widely used technique for coherent population transfer in
atoms and molecules [1]. Because STIRAP is an adiabatic
technique it is insensitive to small to moderate variations in
most of the experimental parameters. A particularly remarkable and
very useful feature of STIRAP is its insensitivity to the
properties of the intermediate state $\psi_2$. For these reasons
STIRAP is a very attractive technique for quantum information
processing (QIP) [3,4]. However, it is
widely recognized that QIP requires very high fidelities, with the
admissible error of gate operations being below $10^{-4}$ for a
reliable quantum processor [5,6].
Utilizing a recent idea of Guerin \emph{et al.} [7] who
applied the well-known Dykhne-Davis-Pechukas (DDP) method
[8] to optimize adiabatic passage in a two-state
system, we propose how to achieve an ultrahigh fidelity in STIRAP,
and thus make it fully suitable for QIP. In order to adapt this
approach to STIRAP, we reduce the three-level Raman system to
effective two-state systems in two limits: on exact resonance and
for large single-photon detuning. The optimization, which
minimizes the nonadiabatic transitions and maximizes the fidelity,
leads to a particular relation between the pulse shapes of the
driving pump and Stokes fields. The DDP-optimized version of
STIRAP maintains its robustness against variations in the pulse
intensities and durations, the single-photon detuning and possible
losses from the intermediate state.

[1] U. Gaubatz, P. Rudecki, S. Schiemann, K. Bergmann, J. Chem. Phys. \textbf{92}, 5363 (1990);
S. Schiemann, A. Kuhn, S. Steuerwald, K. Bergmann, Phys. Rev.
Lett. \textbf{71}, 3637 (1993).\newline
%
[2] N. V. Vitanov, M. Fleischhauer, B. W. Shore and K. Bergmann, Adv. At. Mol. Opt. Phys. \textbf{46}, 55 (2001);
N. V. Vitanov, T. Halfmann, B. W. Shore and K. Bergmann, Ann. Rev.
Phys. Chem. \textbf{52}, 763 (2001); J. Klein, F. Beil, and T.
Halfmann, Phys. Rev. A \textbf{78}, 033416 (2008).\newline
%
[3] M. Hennrich, T. Legero, A. Kuhn and G. Rempe, Phys. Rev. Lett.
\textbf{85}, 4872 (2000); A. Kuhn, M. Hennrich, and G. Rempe,
Phys. Rev. Lett. \textbf{89}, 067901 (2002).\newline
%
[4] Z. Kis and F. Renzoni, Phys. Rev. A \textbf{65}, 032318 (2002); X.
Lacour, S. Gu\'{e}rin, N. V. Vitanov, L. P. Yatsenko and H. R.
Jauslin, Opt. Commun. \textbf{264}, 362 (2006); C. Wunderlich, T.
Hannemann, T. K\"{o}rber, H. H\"{a}ffner, C. Roos, W. H\"{a}nsel,
R. Blatt and F. Schmidt- Kaler, J. Mod. Opt. \textbf{54}, 1541
(2007).\newline
%
[5] M. A. Nielsen and I. L. Chuang, \emph{Quantum Computation and Quantum Information} (Cambridge University Press, 1990).\newline
%
[6] P. W. Shor, 37th Symposium on Foundations of
Computing 56--65 (IEEE Computer Society Press, Washington DC,
1996); A. Steane, Rep. Prog. Phys. \textbf{61}, 117 (1998); E.
Knill, Nature \textbf{434}, 39 (2005); J. Benhelm, G. Kirchmair,
C. F. Roos and R. Blatt, Nature Phys. \textbf{4}, 463 (2008).\newline
%
[7] S. Gu\'{e}rin, S. Thomas, and H. R. Jauslin, Phys. Rev. A \textbf{65}, 023409 (2002);
 X. Lacour, S. Gu\'{e}rin and H. R. Jauslin, Phys. Rev. A \textbf{78}, 033417 (2008).\newline
%
[8] J. P. Davis and P. Pechukas, J. Chem. Phys. \textbf{64}, 3129 (1976);
 A. M. Dykhne, Sov. Phys. JETP \textbf{11}, 411 (1960).\newline
%
[9] B. W. Shore, \emph{The Theory of Coherent Atomic Excitation} (Wiley, New York, 1990).\newline
%
[10] N. V. Vitanov and S. Stenholm, Opt. Commun. \textbf{127}, 215 (1996).\newline

\vspace{\baselineskip}