\title{ROBUST CONTROL OF LINEAR AND NON-LINEAR QUANTUM SYSTEMS BY SHAPED PULSES}
% Robust control of linear and non-linear quantum systems by shaped pulses

\underline{S. Guerin} \index{Guerin S.}
%Stephane Guerin

{\normalsize{\vspace{-4mm}
Laboratory ICB - University Bourgogne - France



\email sguerin@u-bourgogne.fr}}

The control of quantum systems by external fields (laser) possibly combined with cavity QED or plasmonic field is at the heart of modern applications ranging from quantum information processing to the control of chemical reactions.  It can be in general formulated as the transfer from an initial to a target state for photonic [1], atomic [2], molecular [3], and quantum dot states [4].

One challenging issue is the ability to achieve a high-fidelity transfer to a given target state in a robust way with respect to fluctuations, the partial knowledge of the system, and decoherence. This can be achieved by the single-shot shaped pulse technique [5-7], which extends the composite pulse method [8]. Its extension to non-linear quantum systems, such as the one featuring the production of molecular Bose-Einstein condensates from atomic ones, is presented [9].

{\normalsize
[1] A. Gogyan, S. Guerin, C. Leroy, and Yu. Malakyan, Phys. Rev. A \textbf{86}, 063801 (2012).
\vsp

[2] B. Rousseaux, S. Guerin, and N.V. Vitanov, Phys. Rev. A \textbf{87}, 032328 (2013).
\vsp

[3] M. Sala,  M. Saab, B. Lasorne, F. Gatti, and S. Guerin, J. Chem. Phys. \textbf{140}, 194309 (2014).
\vsp

[4] B. Rousseaux, D. Dzsotjan, G. Colas des Francs, H.R. Jauslin, C. Couteau, and S. Guerin, Physical Review B \textbf{93}, 045422 (2016); Erratum, Phys. Rev. B \textbf{94}, 199902 (2016).
\vsp

[5] D. Daems, A. Ruschhaupt, D. Sugny, and S. Guerin, Phys. Rev. Lett. \textbf{111}, 050404 (2013).
\vsp

[6] L. Van-Damme, D. Schraft, G.T. Genov, D. Sugny, T. Halfmann, and S. Guerin, Phys. Rev. A \textbf{96}, 022309 (2017).
\vsp

[7] H. Jo, H. Lee, S. Guerin, and J. Ahn, Phys. Rev. A \textbf{96}, 033403 (2017).
\vsp

[8] B.T. Torosov, S. Guerin, N.V. Vitanov, Phys. Rev. Lett. \textbf{106}, 233001 (2011).
\vsp

[9] V. Dorier, M. Gevorgyan, A. Ishkhanyan, C. Leroy, H.R. Jauslin, and S. Guerin, Phys. Rev. Lett. \textbf{119}, 243902 (2017).
}

\vspace{\baselineskip} 