\title{PROPAGATION OF LIGHT POLARIZATION IN A BIREFRINGENT MEDIUM: EXACT ANALYTIC MODELS}

\underline{G. T. Genov}, A. A. Rangelov, and N. V. Vitanov
\index{Genov G} \index{Rangelov A} \index{Vitanov N}

{\normalsize{
\vspace{-4mm} \unisofia

\email genko.genov@phys.uni-sofia.bg}}

We use the analogy between the torque equation of motion and coherent atomic excitation of a two state system to describe the evolution of the Stokes polarization vector in a birefringent medium without polarization dependent loss [1]. We give exact analytic solutions for this evolution when the birefringent vector corresponds to the dynamics of quantum two-state systems, which are described by the one-dimensional (resonance) model, the Landau-Zener model [2], and the Demkov-Kunike model [3-4]. Finally, we demonstrate how this method can be applied for broadband conversion of light polarization in analogy to rapid adiabatic passage (RAP) in two-state quantum systems [5].

In addition to polarization manipulation, this approach can also be useful in many other branches of physics where we need exact analytic solutions to a torque equation. These include the description of the Newton equation of motion, the classical motion of a charged particle in oscillating magnetic and electric fields, e. g. for charged particle confinement, optical waveguides, polychromatic beam splitter, sum frequency conversion techniques in nonlinear optics, the dynamics of a spin in a magnetic field, and the behavior of a gyroscope acted on by gravity.


{\normalsize
[1] H. Kubo, R. Nagata, Opt. Commun. \textbf{34}, 306 (1980).
\vsp

[2] C. Zener, Proc. R. Soc. London A \textbf{137}, 696 (1932).
\vsp

[3] N. Rosen, C. Zener, Phys. Rev. \textbf{40}, 502 (1932).
\vsp

[4] Yu. Demkov, M. Kunike, Vestn. Leningr. Univ. Fiz. Khim. \textbf{16}, 39 (1969).
\vsp

[5] B. W. Shore, The Theory of Coherent Atomic Excitation, New York, 1990.
}

\vspace{\baselineskip} 