\title{SPATIAL MULTI-PHOTON INTERFERENCES WITH THERMAL LIGHT SOURCES}

\underline{S. Oppel} \index{Oppel S}

{\normalsize{\vspace{-4mm}
Universit\"{a}t Erlangen-N\"{u}rnberg, Institut f\"{u}r Optik,
Information und Photonik, Erwin-Rommel-Str. 1, MZB 105 91058, Erlangen


\email steffen.oppel@physik.uni-erlangen.de}}

We report the observation of multi-photon interferences up to fifth order of photons emitted by independent thermal sources (TLS). We compare the corresponding multi-photon signals to those obtained by single photon emitters (SPE). For equal numbers of TLS and detectors, placed at certain detector positions $\mathbf{r}_1,\ldots ,\mathbf{r}_N$, the normalized $N$th order spatial intensity correlation function $g^{(N)}_{\text{TLS}}(\mathbf{r}_1, \ldots ,\mathbf{r}_N)$ as a function of $\mathbf{r}_1$ reveals a pure sinusoidal fringe pattern. A detailed quantum field theoretical description shows that for this kind of modulation the same interference terms contribute to the multi-photon signal as those obtained from $N$ SPE. However, for the latter the signal exhibits a visibility of 100\%. The flexibility of positioning and scanning the $N$ detectors allows to measure a variety of different fringe patterns. For example, depending on whether one or two detectors are scanned and whether in case of two detectors they are moved simultaneously in the same or in opposite directions, the correlation function $g^{(N)}_{\text{TLS}}(\mathbf{r}_1)$ displays interference patterns oscillating at $M \leq N-1$ times the frequency of the corresponding coherent double slit interference signal. This shows that by measuring higher-order correlation functions in the introduced setup it is possible to extract particular spatial frequencies from the $g^{(N)}_{\text{TLS}}(\mathbf{r}_1)$ function.

\vspace{\baselineskip} 