\title{ION TRAPS FOR DETERMINISTIC ION IMPLANTATION AND SCALABLE QUANTUM INFORMATION}

\underline{K. Singer} \index{Singer K}

{\normalsize{\vspace{-4mm}}
Institut f\"{u}r Physik, Staudingerweg 7, 55128 Mainz

\email kilian.singer@uni-mainz.de}

Novel ion trap geometries are presented which are obtained by optimized field calculation and inverse methods [1]. On the first part of the talk our resent progress with a segmented ion trap with mK laser cooled ions is presented which serves as a high resolution deterministic single ion source which can operate with a huge range of sympathetically cooled ion species, isotopes or ionic molecules. We have deterministically extracted a predetermined number of ions on demand [2]. Then planar and three dimensional trap geometries are presented which allow for the application of variable rf fields for transport and splitting operations are presented [3]. These geometries could be of interest for realizing two dimensional ion crystals with controllable interaction and enable novel schemes for quantum simulation.

{\normalsize
[1] K. Singer, U. G. Poschinger, M. Murphy, P. A. Ivanov, F. Ziesel, T. Calarco, F. Schmidt-Kaler, Rev. Mod. Phys. \textbf{82}, 2609 (2010).%\newline
\vsp

[2] W. Schnitzler, N. M. Linke, R. Fickler, J. Meijer, F. Schmidt-Kaler, and K. Singer, Phys. Rev. Lett. \textbf{102}, 070501 (2009).%\newline
\vsp

[3] T. Karin, I. Le Bras, A. Kehlberger, K. Singer, N. Daniilidis, H. H\"{a}ffner, arXiv:1011.6116%\newline
}

\vspace{\baselineskip}
