\title{EXACT SOLUTION OF THE OPTICAL BLOCH EQUATION FOR THE DEMKOV MODEL}

\underline{G. S. Vasilev}$^{1}$ and N. V. Vitanov$^{1,2}$
\index{Vasilev G}\index{Vitanov N}

{\normalsize{

\vspace{-4mm} $^1$\unisofia

\vspace{-4mm} $^2$ Institute of Solid State Physics, Bulgarian
Academy of Sciences, Tsarigradsko chauss\'{e}e 72, 1784 Sofia,
Bulgaria 2


\email vasilev@phys.uni-sofia.bg}}

Coherent excitation influenced by dephasing processes represents
an important topic in quantum mechanics [1]. Applications of such
models are numerous ranging from coherent atomic excitation and
quantum information to chemical physics and solid-state physics.
Although a significant effort have been devoted for studding the
Bloch equations corresponding to specific two-state models, almost
all results are related to some asymptotic regimes as weak
dephasing, strong coupling or other limits [2]. There are very few
exact solutions for the Bloch equation. The complexity of this
problem is due to the difficulty of deriving an exact solution for
third order linear differential equations. In the case of resonant
coherent excitation of a two-state system in the the presence of
dephasing, solution can be found in [3]. This work
presents an exact analytic solution for coherent excitation of a
two-state quantum system driven by a time-dependent pulsed
external field described by Demkov model in the presence of
dephasing. The solution is expressed in terms of Generalized
hypergeometric functions.

{\normalsize
[1] B. W. Shore, The Theory of Coherent Atomic Excitation, New York, 1990.
\vsp

[2] X. Lacour, S. Gu\'erin, L. P. Yatsenko, N. V. Vitanov and H.-R.
Jauslin, Phys. Rev. A \textbf{75}, 033417 (2007).
\vsp

[3] E. S. Kyoseva and N. V. Vitanov, Phys. Rev. A \textbf{71}, 054102 (2005).
}

\vspace{\baselineskip}
