\title{DRESSED ADIABATIC TRAPS FOR COLD ATOMS: GOING BEYOND LANDAU-ZENER}
% Dressed adiabatic traps for cold atoms: going beyond Landau-Zener

\underline{B. Garraway} \index{Garraway B}
%Barry Garraway

{\normalsize{\vspace{-4mm}
Department of Physics and Astronomy
University of Sussex,
United Kingdom

\email b.m.garraway@sussex.ac.uk}}

Dressing atoms with radio-frequency and microwave radiation opens up new possibilities for the adiabatic trapping of cold atoms and condensates in new topologies such as spherical surfaces, wave-guide loops [1,2] and (non-optical) lattices [3,4].  This is because of the flexibility inherent in the vector coupling of a magnetic dipole moment to electromagnetic fields which can be varied in time, frequency, orientation and space. This may in turn result in quantum technology applications to sensing (with ring traps and gyroscopes [5,6]), metrology, interferometry and atomtronics.  This presentation will give a brief overview of the development of the field before focussing on our latest work on the application of the Landau-Zener model to the the adiabatic trapping problem [7].  It is found that, when carefully implemented, the Landau-Zener theory overestimates the rate of non-adiabatic spin flip transitions in the adiabatic limit.  This indicates that care is needed when determining requirements for practical atom traps.

{\normalsize
[1] B. M. Garraway and H. Perrin, J. Phys. B \textbf{49}, 172001 (2016);
\vsp

[2] H. Perrin and B. M. Garraway, in Advances in Atomic, Molecular and Optical Physics, \textbf{66} (Academic Press, 2017), in press;
\vsp

[3] G. A. Sinuco-Leon and B. M. Garraway, New J. Phys. \textbf{17}, 053037 (2015);
\vsp

[4] G. A. Sinuco-Leon and B. M. Garraway, New J. Phys. 18, 035009 (2016);
\vsp

[5] O. Morizot, Y. Colombe, V. Lorent, H. Perrin, and B. M. Garraway, Phys. Rev. A \textbf{74}, 023617 (2006);
\vsp

[6] G. Sinuco-Leon, K. Burrows, A. S. Arnold, and B. M. Garraway, Nat. Commun. \textbf{5}, 5289 (2014);
\vsp

[7] K. Burrows, B.M. Garraway and H. Perrin, arxiv:1705.00681, submitted (2017).
}

\vspace{\baselineskip} 