\title{COHERENT CONTROL OF TRAPPED RYDBERG IONS}
% Coherent control of trapped Rydberg ions

\underline{M. Hennrich} \index{Hennrich M}
%Markus Hennrich

{\normalsize{\vspace{-4mm}
Department of Physics, Stockholm University,
Albanova University Center,
Roslagstullsbacken 21,
10691 Stockholm, Sweden

\email markus.hennrich@fysik.su.se}}

Trapped Rydberg ions are a novel quantum system [1]. By combining the high degree of control of trapped ion systems with the long-range dipole-dipole interactions of Rydberg atoms [2], fast entanglement gates may be realized in large ion crystals [3].
Quantum information processing in this system is envisaged to use low-lying electronic states for storage of qubits and strongly interacting Rydberg states for entanglement operations. This requires the Rydberg excitation to be coherently controlled.
In our experiment [4] we have observed the first coherent Rydberg excitations of an ion via a two-photon excitation to Rydberg S states. Coherent effects observed include Rabi oscillations, EIT and STIRAP. We also report the realization of microwave-dressed Rydberg ions driving the transition between Rydberg S and P states. This marks an important step towards realizing entanglement operations between Rydberg ions, which are envisaged to strongly interact with each other via the large oscillating dipole moments of microwave-dressed Rydberg states.

{\normalsize
[1] M. Müller, et al., New J. Phys. \textbf{10}, 093009 (2008);
\vsp

[2] D. Jaksch, et al., Phys. Rev. Lett. \textbf{85}, 2208 (2000);
\vsp

[3] F. Schmidt-Kaler, et al., New J. Phys. \textbf{13}, 075014, (2011);
\vsp

[4] G. Higgins, et al., arXiv:1611.02184v1 (2016).
}

\vspace{\baselineskip} 