\title{DRESSING ULTRA-COLD ATOMS FOR CIRCUITS, SHELLS AND LATTICES}
% Dressing ultra-cold atoms for circuits, shells and lattices

\underline{B. Garraway} \index{Garraway B.}
%Barry Garraway

{\normalsize{\vspace{-4mm}
Department of Physics and Astronomy,
University of Sussex,
Falmer, Brighton, BN1 9QH, UK



\email b.m.garraway@sussex.ac.uk}}

In quantum optics, the dressed atom proved to be a useful concept for Cohen-Tannoudji and Reynaud in the analysis of resonance fluorescence from an atom back in 1977 [1]. More recently it has been found that by adiabatically dressing atoms with radio-frequency and microwave radiation we can produce a variety of different types of spatial trap for ultra-cold atoms (see reviews in Refs. [2, 3]). In this talk we will see how shell potentials can be fine tuned [4] and the results and applications for probing RF dressed potentials with microwave pulses [5].

{\normalsize
[1] Dressed-atom description of resonance fluorescence and absorption spectra of a multi-level atom in an intense laser beam, C Cohen-Tannoudji and S Reynaud, J. Phys. B \textbf{10}, 345 (1977).
\vsp

[2] Topical Review: Recent developments in trapping and manipulation of atoms with adiabatic potentials, B.M. Garraway and H. Perrin, J. Phys. B \textbf{49}, 172001 (2016).
\vsp

[3] Trapping atoms with radio-frequency adiabatic potentials, H. Perrin and B.M. Garraway, in Advances in Atomic, Molecular and Optical Physics, vol. 66, pp 181-262 (2017).
\vsp

[4] G.A. Sinuco-Leon, N. Lundblad and B.M. Garraway, in preparation.
\vsp

[5] Microwave spectroscopy of radio-frequency dressed 87Rb, G. A. Sinuco-Leon, B. M. Garraway, H. Mas, S. Pandey, G. Vasilakis, V. Bolpasi, W. von Klitzing, B. Foxon, S. Jammi, K. Poulios, and T. Fernholz, Phys. Rev. A \textbf{100}, 053416 (2019).
}

\vspace{\baselineskip}