\title{ULTRAHIGH-FIDELITY ROBUST/SENSITIVE DESIGN OF SINGLE-QUBIT GATES VIA CONVENTIONAL AND MODULATED COMPOSITE PULSES}
% Ultrahigh-Fidelity Robust/Sensitive Design of Single-Qubit Gates via Conventional and Modulated Composite Pulses

\underline{H. Gevorgyan} \index{Gevorgyan H.}
%Hayk Gevorgyan

{\normalsize{\vspace{-4mm}
1164 Sofia, 5 James Bourchier Blvd., Faculty of Physics



\email hayk.gev.yan@gmail.com}}

 Conventional composite pulses are pulse sequences with precisely designed composite phases and pulse areas. In fact, the theory only requires the integrability of the Hamiltonians, which makes modulation of the technique possible. Two cases of ``modulated composite pulses'' are considered --- 1. ``detuned composite pulses'' - Hamiltonians with static non-zero detunings and rectangular Rabi frequencies, 2. ``shaped composite pulses'' - on-resonant Hamiltonians with time-dependent Rabi frequencies. An exotic way is the simultaneous compensation of errors by various independent methods. For example, suppressing the pulse area error using composite pulses (in the total evolution) and, independently, suppressing the off-resonance error (in each pulse evolution) using alternative technique of single-shot-shaped pulses (or otherwise) --- 3. ``hybrid composite pulses''.

 Two different protocols are used to obtain SU(2) single-qubit gates: $\Theta_{\phi}$ rotation gate for the NOT and Hadamard; and $\Phi$ phase gate for $Z$, $S$ and $T$ gates. Optimum orders of robustness are obtained for a certain number of pulses. The purpose of modulation is to get simultaneous error compensation (better than for conventional composite pulses) while maintaining ultrahigh fidelity.
 
 The analysis of various modulated composite pulses and conventional broadbands, as well as a comparison between them are accomplished. Note that some of them provide point-to-point fidelity that can be extended to QIP by averaging over all initial states. The gates optimized by the composite pulses technique are fully-compensating (overall fidelity). They provide broadband flat-top fidelity (like BB1 of Wimperis and SCROFULOUS pulses), guaranteeing ultrahigh accuracy.
 
Narrowband and broadband cases of the above-mentioned approaches can be considered in a similar manner. These general rotations have an enormous number of applications. Using the quantum-classical analogy of Bloch-Poincar\'e spheres, by simple transformation of the control parameters, one can construct ultrahigh-precision robust polarization retarders, rotators and filters as analogues of broadband $\Theta_{\phi}$, $\Phi$ rotations and their narrowbands (in the circular $|LR\rangle$ polarization basis), respectively.

\vspace{\baselineskip}