\title{HIGH ACCURACY OR HIGH SPEED LASER RANGING: A NEW CONCEPT}

\underline{K. Bergmann} \index{Bergmann K}

{\normalsize{\vspace{-4mm}
Fachbereich Physik and OPTIMAS Research Center,
Technische Universit\"{a}t Kaiserslautern, Germany

\email bergmann@rhrk.uni-kl.de}}

Central to this presentation will be the discussion of a novel concept for laser ranging, based
on a frequency-shifted feedback laser (fsf-laser) and suitable for industrial applications. In
a fsf-laser, the typical frequency-space mode structure is overcome by shifting the frequency
of the circulating laser field at each round trip via an acousto-optical frequency shifter and
feeding back only the frequency-shifted part. Injection seeding of such a device with a narrow
band laser leads to a spectral comb-structure in the continuous wave output spectrum (different
from the well known comb structure in the spectrum of mode-locked femto-second lasers). Part of
this radiation field is sent to a reference surface the other to the object. Superposition of
the two coherent multi-component (reflected and scattered) fields on a fast photo diode leads
to a complex response. The latter is simplified when the injected laser is phase modulated. The
detector response is monitored as the modulation frequency is tuned. At a specific modulation
frequency all the components contributing to the signal are in phase and a signal, orders of
magnitude above the noise floor, results. The distance of the object is easily and accurately
derived form the modulation frequency, leading to this maximum. Depending in the layout of the
fsf-laser system, an accuracy of about 1 micrometer over distances of a few meters (with $>$ 1 kHz
rate of data taking) or 1 mm over distances of several ten meters (with about 1 MHz rate of
data taking) can be achieved.

\vspace{\baselineskip}
