\title{COHERENT CONTROL OF ULTRAFAST ELECTRON DYNAMICS}

\underline{M. Wollenhaupt} \index{Wollenhaupt M}

{\normalsize{\vspace{-4mm}
Carl von Ossietzky Universit\"{a}t Oldenburg,
Carl-von-Ossietzky-Stra{\ss}e 9-11,
D-26129 Oldenburg, Germany 

\email matthias.wollenhaupt@uni-oldenburg.de}}

Using shaped ultrashort laser pulses of controllable envelope and instantaneous frequency with zeptosecond precision [1] allows to manipulate the electron dynamics of quantum systems with unprecedented accuracy. In order to demonstrate three-dimensional control with polarization-shaped laser pulses we have developed a tomographic reconstruction method to measure the three-dimensional photoelectron angular distributions (PAD) in a Velocity Map Imaging (VMI) set-up. We have demonstrated the creation of designer free-electron wave packets [2,3]. In addition, we present a femtosecond laser-based approach to chiral recognition of randomly oriented chiral molecules in the gas phase. PAD resulting from REMPI of small chiral organic molecules are studied. The observed asymmetry in the PAD using left- and right-handed circularly polarized femtosecond laser pulses, i.e. the Photoelectron Circular Dichroism (PECD), is in the 10 percent regime [6,7].

{\normalsize
[1] J. K\"{o}hler, M. Wollenhaupt, T. Bayer et al., Opt. Express \textbf{19}, 11638 (2011).
\vsp

[2] M. Wollenhaupt, C. Lux, M. Krug et al., Chem. Phys. Chem. \textbf{14}, 1341 (2013).
\vsp

[3] P. Hockett, M. Wollenhaupt, C. Lux et al., Phys. Rev. Lett. \textbf{112}, 223001 (2014).
\vsp

[4] T. Bayer, H. Braun, C. Sarpe et al., Phys. Rev. Lett. \textbf{110}, 123003 (2013).
\vsp

[5] H. Braun, T. Bayer, C. Sarpe et al., J. Phys. B \textbf{47}, 124015 (2014).
\vsp

[6] C. Lux, M. Wollenhaupt, T. Bolze et al., Angew. Chem. Int. Ed. \textbf{51}, 5001 (2012).
\vsp

[7] C. Lux, M. Wollenhaupt, C. Sarpe et al., Chem. Phys. Chem. \textbf{16}, 23 (2015).
}

\vspace{\baselineskip}
